JavaScript as an Embedded DSL

### 2012-03-29 papers/ecoop2012/article.tex
change code url
Fix messed up listing.
Added a mention of play validators in evaluation.

Here is the JavaScript code generated for this snippet:
\begin{lstlisting}[language=JavaScript]
function test(x0) {
  var x6 = []
  for(var x1=0;x1<x0;x1++){
    var x4 = []
    for(var x2=0;x2<x0;x2++){
      var x3 = x1 * x2
      x4[x2]=x3
    }
    x6.splice.apply(x6, [x6.length,0].concat(x4))
  }
  return x6
}

@@

\end{lstlisting}

@@

We've implemented our DSL in Scala.\footnote{The code can be found at
  \url{http://github.com/namin/lms-sandbox}} We used our DSL to
develop a few web applications, which are simple but not
trivial. First, we implemented a few drawing examples like the
snowflakes of figure~\ref{fig:snowflakes}. We extended the Twitter
example from section~\ref{sec:cps}, which presents the latest tweets
from selected users in an interactive way. In order to do so, we
incorporated a useful subset of the DOM API and jQuery library using our
typed APIs.

>>>>

Here is the JavaScript code generated for this snippet:
\begin{lstlisting}[language=JavaScript]
function test(x0) {
  var x6 = []
  for(var x1=0;x1<x0;x1++){
    var x4 = []
    for(var x2=0;x2<x0;x2++){
      var x3 = x1 * x2
      x4[x2]=x3
    }
    x6.splice.apply(x6, [x6.length,0].concat(x4))
  }
  return x6
}
\end{lstlisting}

@@

@@

We've implemented our DSL in Scala.\footnote{The code can be found at
  \url{http://github.com/js-scala}} We used our DSL to
develop a few web applications, which are simple but not
trivial. First, we implemented a few drawing examples like the
snowflakes of figure~\ref{fig:snowflakes}. We extended the Twitter
example from section~\ref{sec:cps}, which presents the latest tweets
from selected users in an interactive way. In order to do so, we
incorporated a useful subset of the DOM API and jQuery library using our
typed APIs.

Also, we integrated our DSL with an existing web framework, Play 2.0.\footnote{http://www.playframework.org/}
Our DSL can be used to define Play form validators that are executed both at the client and the server side.
We managed to achieve that without deep changes to how the framework works internally proving that our
DSL can be used as a library.
